Robust background subtraction in traffic environments

### 2019-02-21 paper/Paper.tex
24h description paper

@@

\begin{table}[]
\begin{tabular}{l|c}
    Algorithm                                     & Average time \\
    \hline
    PBAS on grayscale video                       & 90ms         \\
    PBAS on RBG video                             & 180ms        \\
    PBAS on RBG video with optical flow analysis  & 200ms        
\end{tabular}
\end{table}

>>>>

\begin{figure}[!t]
    \centering
    \subfloat[][00:06:00]{
        \includegraphics[width=0.45\textwidth]{Figures/24h_1.jpg}
    }
    \newline
    \subfloat[][00:28:00]{
        \includegraphics[width=0.45\textwidth]{Figures/24h_2.jpg}
    }
    \newline
    \subfloat[][00:45:00]{
        \includegraphics[width=0.45\textwidth]{Figures/24h_3.jpg}
    }
    \newline
    \subfloat[][01:00:00]{
        \includegraphics[width=0.45\textwidth]{Figures/24h_4.jpg}
    }
    \newline
    \subfloat[][01:23:00]{
        \includegraphics[width=0.45\textwidth]{Figures/24h_5.jpg}
    }
    \caption{It is shown how the algorithm adapts to change of lightining and traffic conditions during a 1h and 30 min video sample.}
\end{figure}

@@

\begin{table}[]
\begin{tabular}{l|c}
    Algorithm                                     & Average time \\
    \hline
    PBAS on grayscale video                       & 90ms         \\
    PBAS on RBG video                             & 180ms        \\
    PBAS on RBG video with optical flow   & 200ms        
\end{tabular}
\end{table}
